paper

### 2021-10-21 paper.Rmd
as

```{r}
epred1_111 %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        axis.title.x = element_blank(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig1

ggsave("figures/Figure 2.png", width = 5, height = 4)
```

@@

```{r}
epred2_222 %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        axis.title.x = element_blank(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig2

ggsave("figures/Figure 22.png", width = 5, height = 4)
```

@@

```{r}
fig1 / fig2 / fig3 +
  plot_annotation(tag_levels = 'A')

ggsave("figures/Figure 2.png", width = 6, height = 12)
```

@@

```{r}
epred1_1 %>% 
  bind_rows(epred2_2) %>% 
  bind_rows(epred5) |> 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred_wt
```

@@

```{r}
epred4_wt1 %>%
  ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 size = 1.2) +
  coord_flip() +
  geom_text_repel(aes(label = round(emmean,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
  scale_color_calc() +
  scale_y_continuous(limits = c(0,75), breaks = seq(0, 75, 15)) +
  labs(x = NULL, y = expression(paste("Soybean yield (bu acre"^"-1",")"))) +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig2

ggsave("figures/Figure 4.png", width = 6, height = 4)
```

>>>>

```{r}
epred1_111 %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        axis.title.x = element_blank(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F9F6EE"),
        panel.background = element_rect(fill = "#F9F6EE"),
        axis.text = element_markdown(color = "#333333")) -> fig1

#ggsave("figures/Figure 2.png", width = 5, height = 4)
```

@@

```{r}
epred2_222 %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        axis.title.x = element_blank(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F9F6EE"),
        panel.background = element_rect(fill = "#F9F6EE"),
        axis.text = element_markdown(color = "#333333")) -> fig2
#ggsave("figures/Figure 22.png", width = 5, height = 4)
```

@@

```{r}
fig1 / fig2 +
  plot_annotation(tag_levels = 'A')

ggsave("figures/Figure 3.png", width = 6, height = 8)
```

@@

```{r}
epred1_1 %>% 
  bind_rows(epred2_2) %>% 
#  bind_rows(epred5) |> 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred_wt
```

@@

```{r}
epred4_wt1 %>%
  ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 size = 1.2) +
  coord_flip() +
  geom_text_repel(aes(label = round(emmean,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
  scale_color_calc() +
  scale_y_continuous(limits = c(0,75), breaks = seq(0, 75, 15)) +
  labs(x = NULL, y = expression(paste("Soybean yield (bu acre"^"-1",")"))) +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11),
        legend.position = "none",
        plot.background = element_rect(fill = "#F9F6EE"),
        panel.background = element_rect(fill = "#F9F6EE"),
        axis.text = element_markdown(color = "#333333")) -> fig2

ggsave("figures/Figure 5.png", width = 6, height = 4)
```
